\section{Material acquisition (related work)}

Material acquisition is the task of recovering the intrinsic properties of materials based on their appearance. It is of great importance in many applications. For example, tumors can be detected and classified as malignant or non-malignant \cite{boas2001imaging}; important blood properties such as red and white blood counts can also be analyzed \cite{berne2000dynamic, durduran2010diffuse}; in materials science, material acquisition is used to validate the fidelity and shelf life of material samples \cite{sumin2019geometry}; and the chemical compositions of nanodispersions can be inferred for particle sizing applications \cite{pine1990diffusing}. Material acquisition methods can be grouped into three categories depending on the ratio of the mean free path (expected distance traveled by a photon in the medium) to the characteristic size of the scattering volume. We summarize these categories in turn, as well as several common phase function models.

Inverse radiative transport \cite{bal2009inverse} is studied heavily in graphics as well as the physical and biomedical sciences. While inverse radiative transport methods for scattering media fall into three main categories, methods using the \textit{diffusion} approximation focus on optically thick media where high-order scattering is dominant. While this approximation simplifies inference and is suitable for both homogeneous and heterogeneous materials \cite{farrell1992diffusion, munoz2011bssrdf, papas2013fabricating}, it introduces parameter ambiguities. Similarity relations are hierarchical parameter relationships that allow scattering parameters to be altered without significantly altering the medium's spatial properties. These relations can be derived from transport equations to accelerate Monte Carlo simulations \cite{wyman1989similarity}. However, a radiance field computed via Monte Carlo simulations can be described by multiple, distinct sets of parameters, and finding mulutiple candidate solution sets is generally challenging. Parameter space warping and exploiting similarity relations have improved the efficiency of iterative solvers \cite{zhao2014high}.

Rather than focusing purely on high-order scattering, another class of methods considers all paths of arbitrary lengths. Given a set of input images, they estimate material parameters whose combinations closely match the inputs when simulated using Monte-Carlo rendering \cite{dutre2018advanced, novak2018monte}. Differentiable rendering determines the effects of changes in scattering parameters by estimating derivatives of images. Traditionally, these estimtes have been approximate models that ignore complex light transport effects such as subsurface scattering and inter-reflections \cite{loper2014opendr}. Differentiable Monte Carlo rendering overcomes these limiations by computing derivatives while accounting for all light transport effects \cite{gkioulekas2016evaluation, gkioulekas2013inverse, khungurn2015matching, nimier2020radiative, nimier2019mitsuba}. Machine learning approaches offer lower computational complexity at the cost of reduced robustness and diminished physically accurate solutions. Encoder networks can be paired with Monte Carlo renderers to improve their generalization to scenes with unseen geometry and light sources \cite{wu2017neural, che2020towards}. Energy losses in neural radiance fields are mitigated by efficient indirect illumination estimation via spherical harmonics \cite{zheng2021neural}. While these approach are more general in nature and can handle arbitrarily thick materials, they are computationally expensive and require proper initialization.

The final class of methods are based on the \textit{single scattering} approximation. The first approach assumes the medium is thin enough optically such that photons only scatter once when traveling through the medium. Since the scattering phase function is defined in terms of single-scattering, this allows the phase function to be observed directly. Although this method is as simple, it is limited to a narrow classes of materials such as gases and liquids of low viscosity \cite{narasimhan2006acquiring}. Viscous liquids and thin solids can be acquired by illuminating materials with coherent light and computing the correlations of speckle images. Speckle image correlations are dominated by single-scattered light, and \cite{alterman2022direct} showed that the phase function is proportional to the square root of the correlation and can be computed using a closed-form equation. However, this method is limited to measuring phase functions up to $8^\circ$ due to aberrations.

The Henyey-Greenstein model is used widely due to its relative flexibility considering it is a single-parameter model \cite{henyey1940diffuse}. It is controlled by an anisotropy parameter $g \in [-1, 1]$ that can be used to model backward and forward scattering. However, its simplicity limits its ability to accurately model other scattering regimes such as Rayleigh scattering that occurs when scattering particles are small compared to the wavelength \cite{cornette1992physically, rayleigh1899xxxiv}. Alternatives to this model include using linear combinations of two Henyey-Greenstein lobes (forward and backward) as well as a two-parameter model for highly anisotropic scattering present in human blood \cite{reynolds1980approximate}. However, there remain common materials that are not well-represented by these models such as soaps and waxes \cite{gkioulekas2013understanding}. Hara et al. modify the HG phase function by adding side-lobes resembling the von Mises-Fisher distribution which closely resembles scattering of materials such as soaps and waxes that exhibit forward scattering with significant side scattering \cite{fisher1953dispersion, hara2007mixture}.