\section{Material representation and acquisition}

\paragraph{Representation} Scattering materials are generally composed of small particles with varying refractive properties we describe through the bulk statistical properties of the material. We use three statistical properties to parameterize the scattering material. The extinction coefficient describes the extinction cross-section of the scattering particles per unit volume. It is therefore proportional to the density of scattering particles inside the material. The extinction coefficient is the sum of the absorption and scattering coefficients $\sigma_t = \sigma_a + \sigma_s$ which represent, respectively, the portion of light absorbed and scattered per unit length along the path. The material's phase function $\rho(\arccos(\uvec{i} \cdot \uvec{v}))$ describes the directionality of scattered light and determines the portion of light scattered towards direction $\uvec{v}$ when a scatterer is illuminated from direction $\uvec{i}$. A scatterer's phase function is dictated by its shape and refractive index. Phase functions for spherical particles can be computed analytically using Mie theory\cite{bohren2008absorption, frisvad2007computing, hulst1981light}. $\rho$ is generally assumed to be isotropic. This means its value depends only on the inner product of the illumination and viewing directions, and not on the absolute directions. This may be relaxed by adding an anisotropy parameter $-1 \leq g \leq 1$ where $g=-1$ corresponds to fully backward scattering, $g=0$ means light is scattered equally in all directions, and $g=1$ is full forward scattering. The mean free path (MFP) of a material is defined as the average distance light travels inside the volume between two successive scattering events. The MFP is the inverse of the extinction coefficient $MFP=1/\sigma_t$. When working with scattering volumes, it is common to express its geometric dimensions with respect to the MFP. For example, a volume with optical depth $OD = 4$ means its thickness is $4 \cdot MFP$. This means that light traveling through the medium is scattered four times in average.

Our work is primarily interested in the phase function $\rho$ and will not discuss scattering coefficients. Our work seeks to acquire $\rho$ as a general function and does not assume common parameterizations such as the Henyey-Greenstein phase function \cite{henyey1940diffuse}.

\paragraph{Phase function from single scattering models}
A simple method for measuring phase functions is acquiring optically thin samples that scatter light once on average ($OD \approx 1$). This method is as simple as reflectometry: we illuminate a sample in direction $\vec{i}$ and measure the light received in direction $\vec{v}$, and the phase function is the portion of energy corresponding to scattering angle $\arccos(\uvec{i} \cdot \uvec{v})$. In the paraxial regime, we can apply the small-angle approximation to equate the scattering angle as the norm of the displacement vector between the illuminating and viewing directions $\vec{\tau} = \uvec{v} - \uvec{i}$, and $ |\vec{\tau}| = \arccos(\uvec{i} \cdot \uvec{v})$. This method fails with increasing material thickness due to multiple scattering.
